Discrete Quantum Theories and Computing

### 2018-02-18 dissertation.tex
dissertation.tex Updating according to the current format of document class...

\documentclass[twoside]{iuphd}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}
%\usepackage[basic]{complexity}
\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
\newlang{\usat}{UNIQUE-SAT}
\usepackage[all]{xy}
\usepackage{framed}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[braket,qm]{qcircuit}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{pdfpages}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\says{purple}{Yu-Tsung}{#1}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\gmult}{*}
\newcommand{\Fpx}[1]{\mathbb{F}_{#1}}
\newcommand{\Fq}{\mathbb{F}_{q}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}

\begin{document}
%data for Title Page
\title{Discrete Quantum Theories and Computing}
\author{Yu-Tsung Tai}
\date{\today}
\maketitle[Department of Mathematics][Department of Computer Science]

%data for Acceptance Page
\defensedate{Defense Date}
\acceptancepage{Amr A. Sabry, PhD}{Dylan Paul Thurston, PhD}{Gerardo Ortiz, PhD}{Andrew J. Hanson, PhD}[Shouhong Wang, PhD]

%data for Copyright Page
\cryear{2018}
\copyrightpage

%\begin{dedication}
%\end{dedication}

\begin{acknowledgments}
The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
technical, financial, or personal aid in the preparation of your thesis or dissertation; as a matter of
courtesy, you would ordinarily mention the members of your committee here, as well as institutions that
provided funding, your typist, or anyone else who helped.
\end{acknowledgments}

%\begin{preface}
%\end{preface}

\begin{abstract}
Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems. 
\end{abstract}
\tableofcontents{}

@@

\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}

>>>>

\documentclass[twoside]{iuphd}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\DeclareUnicodeCharacter{0229}{\c{e}}
\DeclareUnicodeCharacter{00A0}{~}
\usepackage{mmap}
\usepackage{comment}
%\usepackage[basic]{complexity}
\newcommand{\lang}[1]{{\ensuremath{\mathsf{#1}}}}
\newcommand{\newlang}[2]{\newcommand{#1}{\lang{#2}}}
\newlang{\usat}{UNIQUE-SAT}
\usepackage[all]{xy}
\usepackage{framed}
\usepackage[braket,qm]{qcircuit}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{pdfpages}
\usepackage{setspace}

\newcommand{\says}[3]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{#1}{#2 says: #3}\end{minipage}\end{framed}}
\newcommand{\muB}{\ensuremath{\mu^{B}}}
\newcommand{\events}{\ensuremath{\mathcal{E}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}\mathrel{}\middle|\mathrel{}{#2}\right\} }}
\newcommand{\gmult}{*}
\newcommand{\Fpx}[1]{\mathbb{F}_{#1}}
\newcommand{\Fq}{\mathbb{F}_{q}}
\newcommand{\ff}[1]{\mathbb{F}_{#1}}

\begin{document}
%data for Title Page
\title{Discrete Quantum Theories and Computing}
\author{\large{Yu-Tsung Tai}}
\date{\today}
\department{Department of Mathematics}
\department{Department of Computer Science}
\maketitle

%data for Acceptance Page
\committeeMember{Amr A. Sabry, PhD}
\committeeMember{Dylan Paul Thurston, PhD}
\committeeMember{Gerardo Ortiz, PhD}
\committeeMember{Andrew J. Hanson, PhD}
\committeeMember{Shouhong Wang, PhD}
\defensedate{Defense Date}
\acceptancepage

%data for Copyright Page
% \cryear{2018}
% \copyrightpage

% \dedication{}
% \dedicationpage

\acknowledgements{The acknowledgments are designed to recognize people or agencies to whom you feel grateful for any academic,
technical, financial, or personal aid in the preparation of your thesis or dissertation; as a matter of
courtesy, you would ordinarily mention the members of your committee here, as well as institutions that
provided funding, your typist, or anyone else who helped.}
\acknowledgementspage

%\preface{}
% \prefacepage

\abstract{Our primary research interest is to build a quantum computing model
characterizing realistic quantum computers. While most of the quantum
computing models based on uncomputable numbers, that is, the continuum
of real numbers, most of the classical computers in our daily life
are digital instead of analog computers. This highlight the necessity
to investigate discrete models for quantum theory and computing. Specifically,
we start from replacing the continuum of complex numbers by the discrete
finite fields. Although we have fruitful results on their geometric
implications and computing powers, their probability models are still
not completely satisfactory. To address this issue, we further exploited
quantum interval-valued probability, and proved an imprecise version
of foundational results such as the Gleason and Kochen-Specker theorems.}
\abstractpage

\tableofcontents{}

@@

\addcontentsline{toc}{chapter}{Bibliography}
\begin{comment}
 \bibliographystyle{plain}
\bibliography{prop}
